% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 
\usepackage[document]{ragged2e}
\usepackage{xcolor}
\usepackage{enumitem}
\begin{document}

\header{Guntas }{Singh Brar}           % Your name

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside} \begin{flushleft} \section{Contact}
    ~
    Mobile no:
    +91 9462546485
    +91 9559185054
    ~
    Email:-
    gbrar@iitk.ac.in
    ~
    Github:-
    guntas1808
    ~
\section{Coursework}
    {\vspace{-0.2cm}} \begin{entrylist}
    {\vspace{-0.5cm}}
    %------------------------------------------------
    \entry
      {* :in progress}
      {\begin{itemize}[leftmargin=*]
          \item Fundamentals
          of Computing 
          {\vspace{+0.12cm}}
          \item Data Structures
          and Algorithms
          {\vspace{+0.12cm}}
          \item Discrete
          Mathematics
         {\vspace{+0.12cm}}
         \item Introduction to 
          Economics
         {\vspace{+0.12cm}}
          \item Linear Algebra 
          and ODE
         {\vspace{+0.12cm}}
          \item Computer 
          Organisation*
            {\vspace{+0.12cm}}
          \item Abstract Algebra*
          {\vspace{+0.12cm}}
          \item Introduction to 
          Mathematical Logic*
          {\vspace{+0.12cm}}
          \item Software 
          Development 
          and Operations*
          {\vspace{+0.12cm}}
          \item Modern Cryptology*
      \end{itemize}} 
    \end{entrylist}
    {\vspace{-0.7cm}}
\section{Responsibilities}
  {\vspace{-0.2cm}}

\begin{entrylist}
{\vspace{-1.1cm}}
%------------------------------------------------
\entry
  {}
  {\begin{itemize}[leftmargin=*]
      \item Secretary,
      DJ War,
      Antargni IIT Kanpur
      (2019)
      {\vspace{+0.12cm}}
      
  \end{itemize}}
  {}
  {}


%------------------------------------------------
%------------------------------------------------

\end{entrylist}
\end{flushleft}
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2018-Present}
{Indian Institute of Technology Kanpur\newline{\normalfont Bachelor of Technology in Computer Science and Engineering}}
{CPI--7.8/10}

%------------------------------------------------
\entry
{April 2018}
{Guru Nanak Public School, Kota\newline{\normalfont AISSCE, CBSE Class XII}}
{Percentage--94.7\%}

\entry
{March 2016}
{Central Academy Senior Secondary School, Bhilwara\newline{\normalfont AISSE, CBSE Class X}}
{CGPA--10.0/10.0}
{\vspace{-0.3cm}}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}

\begin{entrylist}
%------------------------------------------------
\entry
{2019}
{Third Position, {\normalfont IIT Kanpur Summer of Code 2019 among 23 participating teams}}


%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{2018}
{All India Rank 1032, {\normalfont Joint Entrance Examination Advanced, 2018, 2.3 lakh candidates}}


%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{2018}
{All India Rank 2564, {\normalfont Joint Entrance Examination Mains, 2018, 11.5 lakh candidates}}



\end{entrylist}
{\vspace{-0.5cm}}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {2019}
  {Summer of Code, IIT Kanpur}
  {}
  {\jobtitle{Full Stack Developer Intern}
  \begin{itemize}
      \item Developed a web based platform which was designed to make the entire process of the IITK health centre paperless. Interconnected various departments such as the pharmacy, doctor's end, etc.
      \item Built a fully functional website using Django and Bootstrap for frameworks and postgeSQL database management.
  \end{itemize}}
%------------------------------------------------
\entry
  {2018}
  {Electronics Club Winter Workshop, IIT Kanpur}{}
  {\begin{itemize}
      \item Gained theoretical and practical knowledge widely spread over various fields of electronics like ArduinoIDE, FPGAs, etc.
      \item Learnt about data input and processing methods in Computer Vision and Image Processing and basics of Machine Learning.
  \end{itemize}}
%------------------------------------------------
%------------------------------------------------
{\vspace{-0.6cm}}
\end{entrylist}


%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{April 2019}
{Ethical Hacking}
{Association of Computing Activities, IIT Kanpur}
{\begin{itemize}
    \item Learned github, setting up ssh connections and file sharing
    \item Studied Assembly Language, Source Codes, Exploitation of vulnerabilities.
    \item Learned about the basics of cryptology and elementary ciphers.
    \item Practiced through online CTFs such as OverTheWire.
\end{itemize}}
{\vspace{+0.3cm}}
\end{entrylist}
{\vspace{-0.6cm}}
\begin{entrylist}
%------------------------------------------------
\entry
{June 2019}
{Haskell Scrabble Solver}
{Programming Club, IIT Kanpur}
{\begin{itemize}
    \item A implementation project where we learned about functional programming, particularly Haskell
    \item Studied Haskell and practiced with small implementations.
    \item Built a program in Haskell that could solve Scrabble.
\end{itemize}}
{\vspace{-0.3cm}}

\end{entrylist}





%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
  \vspace{-0.3cm}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{\begin{itemize}
    \item Programming Languages: {\normalfont C,C++,Python,Haskell}
    \item Frameworks:            {\normalfont Django, PostgreSQL}
    \item Others:                {\normalfont HTML, CSS, BootStrap, Git, Linux Shell Utilities, AutoDesk}
\end{itemize}}
{}
{}

\end{entrylist}\

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------





\end{document}
